An Improved ANS Transaction Template

### 2018-01-27 paper.tex
almost done with the results

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ by the level and case.}
  \label{tab:cascade_theta}
\end{table}
\end{table} 
As illustrated in Table \ref{tab:cascade_theta}, the effective cut
of each level increases up to $0.54$ for the fifth stage for case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

@@

\subsection{HEU flow rate}

>>>>

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ by the level and case.}
  \label{tab:cascade_theta}
\end{table}
As illustrated in Table \ref{tab:cascade_theta}, the effective cut
of each level increases up to $0.54$ for the fifth stage for case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

@@

\subsection{HEU flow rate}
As shown Figure \ref{fig:heu_prod}, if using all the centrifuges available to
build a big cascade dedicated to HEU production, only 8 months are required to
produce 1 Significant Quantity (SQ) of HEU. Also it take significantly longer to
build 1 SQ of HEU, without recycling the tails respectively 13 years and 3.5 year
for the case 1 and 2 versus about 2 years with tail recycling.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{HEU_prod.png}
  \caption{Evolution of the amount of HEU in the storage. The blue line
  correspond to one significant quantity of HEU ($25~$kg). CX correpsonds to the
  case number(1 or 2), RT and NRT the tail reprocessing or not ones. W/X/Y/Z represent the
  number of cascade per level. REF corresponds to the reference
  case.}\label{fig:heu_prod}
\end{figure}

It is also interresting to note that despite requiering more level of cascade to
reach an enrichment of $90\%$ the second case with tial recycling produces HEU
at a equivalent rate than the case 1. The production rate seems to be faster but
require more time to reach the maximum production rate (the material have to
flow through more levels to reach the final level).
